Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2020-08-03 Manuscript/HI_Model_ms.Rmd
updated manuscript files and retitled supplementary figures

### *States and transitions*
Transition pathways were modified from @daniel_state-and-transition_2016 and @selmants_baseline_2017. Transitions between state types were pre-defined to represent urbanization, agricultural contraction, agricultural expansion, harvesting of tree plantations, and wildfire. Agriculture, forest, grassland, tree plantation, and shrubland state types each had multiple transition pathways, while the barren state type could only transition to urban. Although several state types could transition to urban, there was no transition pathway from urban to any other state type. Water and wetland state types remained static throughout the simulation period. We developed a high and a low land-use scenario, with transition targets based on historical trends of land use change and population projections [@kim_population_2018].

For the high land-use scenario, annual transition targets for agricultural contraction, agricultural expansion, and urbanization were based on

>>>>

### *States and transitions*
We developed a high and a low land-use scenario, with transition pathways modified from @daniel_state-and-transition_2016. Transitions between state types were pre-defined to represent urbanization, agricultural contraction, agricultural expansion, harvesting of tree plantations, and wildfire. Agriculture, forest, grassland, tree plantation, and shrubland state types each had multiple transition pathways, while the barren state type could only transition to developed. Although several state types had urbanization transition pathways, but there was no transition pathway from developed to any other state type. Water and wetland state types remained static throughout the simulation period.

 Transition targets were based on historical trends of land use change from 1992-2011 [@noaa_coastal_2020] and from population projections [@kim_population_2018]. For the high land-use scenario, transition rates for each timestep and Monte Carlo realization were sampled from uniform distributions bounded by the median and maximum historical rates of agricultural contraction, agricultural expansion, and urbanization for each island. For the low land-use scenario, rates of agricultural contraction and expansion were sampled from uniform distributions bounded by zero and the minimum historical rates for each island. Urbanization rates in the low land-use scenario were based on island-level population estimates and projections at five year intervals from 2010-2045 [@kim_population_2018]. We converted population projections into urbanization transition targets following @sleeter_future_2017 by calculating population density for each island and then projecting future developed area based on the five-year incremental change in island population. The spatial extent of agricultural contraction, agricultural expansion, and urbanization was constrained in both land-use scenarios based on existing zoning maps [@daniel_state-and-transition_2016]. Transition targets for tree plantation harvest were set at ~75% of recent historical rates in the high land-use scenario and ~40% of recent historical rates in the low land-use scenario [@daniel_state-and-transition_2016]. In both land-use scenarios, approximately 60% of tree plantation harvests were replacement harvests resulting in conversion of *Eucalyptus* spp. plantations to agriculture. The remaining 40% were rotation harvests.

The wildfire transition sub-model was modified from @daniel_state-and-transition_2016. Historical wildfire size distribution and ignition probabilities for each unique combination of moisture zone (Figure S1), island, and state type (Figure 1) were based on a new 21-year historical wildfire spatial database of the Hawaiian Islands covering the years 1999 to 2019 (Figure S2). The number and size of fires was randomly drawn from one of these historical year-sets for each timestep and Monte Carlo realization, using burn severity probabilities from @selmants_baseline_2017. Wildfire in the low land-use scenario was sampled from the subset of historical fire years at or below the 21-year median area burned statewide; the high land-use scenario sampled from historical fire years above this 21-year median (Fig. S2a).
